Tables for PM2.5 constituents Paper Manuscript

### 2021-11-08 code/data-analysis/config-file-generator.Rmd
Revision
2nd Rev - Mortality Rate - ExpoBuffer PM results

---
title: "Config File Generator"
author: "Fatemeh Kazemi"
date: "01-18-2021"
---

@@

```{r List of Major PM Components Yr Sub}
pmc.major.yr <- c("Yr1_SI","Yr1_NO3","Yr1_SO4",
                "Yr2_SI","Yr2_NO3","Yr2_SO4",
                "Yr3_SI","Yr3_NO3","Yr3_SO4",
                "Yr4_SI","Yr4_NO3","Yr4_SO4",
                "Yr5_SI","Yr5_NO3","Yr5_SO4")
```

@@

```{r ses adj. model for components - bz12 & 1-5yr}
dataname <- "ndi-pmc-bz12-15yr.csv"
expo <- pmc.sub.yr

@@

```{r ses adj. model for components - bz 24 & 1-5yr}
dataname <- "ndi-pmc-bz24.csv"
expo <- pmc.sub.yr

>>>>

---
title: "Config File Generator"
author: "Fatemeh Kazemi"
date: "11-07-2021"
---

@@

```{r List of Major PM Components Yr Sub}
pmc.major.yr <- c("Yr1_SI","Yr1_NO3","Yr1_SO4",
                "Yr2_SI","Yr2_NO3","Yr2_SO4",
                "Yr3_SI","Yr3_NO3","Yr3_SO4",
                "Yr4_SI","Yr4_NO3","Yr4_SO4",
                "Yr5_SI","Yr5_NO3","Yr5_SO4",
                "Yr1_PM", "Yr2_PM", "Yr3_PM", "Yr4_PM", "Yr5_PM")
```

@@

```{r ses adj. model for components - bz12 & 1-5yr}
dataname <- "ndi-pmc-bz12-15yr.csv"
expo <- pmc.major.yr

@@

```{r ses adj. model for components - bz 24 & 1-5yr}
dataname <- "ndi-pmc-bz24-15yr.csv"
expo <- pmc.major.yr

### 2021-11-08 code/data-analysis/output-cleaning.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

---
title: "Analysis Output files"
author: "Fatemeh Kazemi"
date: "01-30-2021"
---

@@

### Source Apportioned PM Mass
mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
  pivot_longer(cols = Biomass:Traffic,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

>>>>

---
title: "Analysis Output files"
author: "Fatemeh Kazemi"
date: "11-07-2021"
---

@@

### Source Apportioned PM Mass
# mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
#   summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
#   pivot_longer(cols = Biomass:Traffic,
#                names_to = "Parameter",
#                values_to = "IQR")%>% 
#   mutate(Parameter = as.factor(Parameter))

### 2021-11-08 code/data-processors/cms-data-processor.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

---
title: "Air Quality and CMS Data"
author: "Fatemeh Kazemi"
date: "1/18/2021"
output: html_document
---
#####To do for fututre/ not urgent in all
##### Fix Factor with and wothout EC names####

@@

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
load(here('data','processed','mass-app-1yr-c2.RDa'))
```

@@

```{r}
cmp.major <- c("SI", "NO3", "SO4")

@@

dt.pmc.major <- dt.pmc1 %>% 
  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
  merge(dt.pmc4) %>% merge(dt.pmc5)

>>>>

---
title: "Air Quality and CMS Data"
author: "Fatemeh Kazemi"
date: "11/07/2021"
output: html_document
---
#####To do for fututre/ not urgent in all
##### Fix Factor with and wothout EC names####

@@

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
load(paste0(dirUSSpatial,'brfss-site.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','master-ndi-pmc-race.RDa'))
load(here('data','processed','master-ndi-pmc-bz6.RDa'))
load(here('data','processed','master-ndi-pmc-bz12.RDa'))
load(here('data','processed','master-ndi-pmc-bz24.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ec-1yr.RDa'))
load(here('data','processed','pmc-residual-1yr.RDa'))
load(here('data','processed','fac-residual-1yr.RDa'))
load(here('data','processed','pmc-sub-5yr.RDa'))
load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
#load(here('data','processed','mass-app-1yr-c2.RDa'))
```

@@

```{r}
cmp.major <- c("SI", "NO3", "SO4", "PM")

@@

dt.pmc.major <- dt.pmc1 %>% 
  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
  merge(dt.pmc4) %>% merge(dt.pmc5)
```

### 2021-11-08 code/data-viz/manuscript-tables.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

---
title: "Tables for PM2.5 constituents Paper Manuscript"
author: "Fatemeh Kazemi"
date: "05/31/2021"
output:
  html_document:
    df_print: paged
---

@@

@@

@@

### Figure S18, S19, S20 - constituents Buffer & Expsoure Window
```{r}
doc <- read_docx()
cmp.major <- c("Si", "NO3", "SO4")
out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
  mutate(Buffer = ifelse(Buffer == "6", "6-mile",
                         ifelse(Buffer == "12", "12-mile", "24-mile")),
         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
         Window = ifelse(Window == "1", "1-yr",
                         ifelse(Window == "2", "2-yr",
                                ifelse(Window == "3", "3-yr",
                                       ifelse(Window == "4", "4-yr", "5-yr")))))

@@

```{r}
print(doc, target = here('output','table','supplement-tables-revision-sescatupd.docx'))
```

>>>>

---
title: "Tables for PM2.5 constituents Paper Manuscript"
author: "Fatemeh Kazemi"
date: "11/07/2021"
output:
  html_document:
    df_print: paged
---

@@

grp <- c('Main', 'Age', 'Sex', 'Race', 'Urbanicity', 'SES.Cat', 'Region', 'BRFSS')

subgrp <- c('Main', '65-75', '> 75', 'Female', 'Male',
            'Asian', 'Black', 'Hispanic', 'White',
            'Urban', 'Rural', 'Low', 'Middle', 'High',
            'West', 'Midwest', 'South', 'Northeast', 'BRFSS')

@@

### Table S3
```{r}
dt.mort.rate <- read.csv(here('output','table','pmc-mortality-rate.csv')) %>% 
  `colnames<-`(c("Group", "Subgroup", cuz)) %>% 
  mutate_at(.vars = cuz, ~as.integer(.x)) %>% 
  mutate(Group = factor(Group, levels = grp),
         Subgroup = factor(Subgroup, levels = subgrp)) %>% 
  arrange(factor(Group, levels = grp), Subgroup)

doc3 <- read_docx()

ft <- flextable(dt.mort.rate)
ft <- merge_v(ft, j = c('Group', 'Subgroup'))
ft <- theme_vanilla(ft)
ft <- vline(ft, j = c('Group', 'Subgroup'))
ft <- padding(ft, padding = 0)
ft <- fontsize(ft, size = 12)
ft <- set_caption(ft, caption = "Table S3. Average monthly cause-specific mortality rate per 100,000 of Medicare enrollees for entire population and by subgroup, US 2000 - 2008.")
ft <- fontsize(ft, i = 1, size = 12, part = "header")
ft <- autofit(ft)

doc3 <- body_add_flextable(doc3, value = ft, split = T)
doc3 <- body_add_par(doc3, "Abbreviations: IHD= Ischemic heart disease; CBV= Cerebrovascular disease; CHF = Congestive heart failure; COPD = chronic obstructive pulmonary disease.", style = "Normal")
body_add(doc3, run_pagebreak())

print(doc3, target = here('output','table','supplement-tables-revision-2nd-mort-rate.docx'))
```

@@

### Figure S18, S19, S20 - constituents Buffer & Expsoure Window
```{r}
doc <- read_docx()
cmp.major <- c("PM2.5", "Si", "NO3", "SO4")
out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
  mutate(Buffer = ifelse(Buffer == "6", "6-mile",
                         ifelse(Buffer == "12", "12-mile", "24-mile")),
         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
         Window = ifelse(Window == "1", "1-yr",
                         ifelse(Window == "2", "2-yr",
                                ifelse(Window == "3", "3-yr",
                                       ifelse(Window == "4", "4-yr", "5-yr")))))

@@

```{r}
print(doc, target = here('output','table','supplement-tables-revision-2nd.docx'))
```
